Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-11-28 formally.tex
rewording comment about composing with reach.

\paragraph{Constructability}
To check that we have defined ``enough'' construct actions, we need to establish that we can start from an empty hole and arrive at any well-typed expression with, for simplicity, the cursor on the outside (Lemma \ref{lemma:reach-down} allows us to then move the cursor anywhere else.) As with reachability, we rely on the iterated action judgements defined in Figure \ref{fig:multistep}.
\begin{theorem}[Constructability]\label{thrm:constructability} ~
  \begin{enumerate}[itemsep=0px,partopsep=0px,topsep=0px]
  \item For every $\htau$ there exists $\bar\alpha$ such that
    $\performTypI{\zwsel{\tehole}}{\bar\alpha}{\zwsel{\htau}}$.

>>>>

\paragraph{Constructability}
To check that we have defined ``enough'' construct actions, we need to
establish that we can start from an empty hole and arrive at any well-typed
expression with the cursor on the outside. This simpler statement is
sufficiently because Lemma \ref{lemma:reach-down} allows us to then move
the cursor anywhere else inside the constructed term. As with reachability,
we rely on the iterated action judgements defined in Figure
\ref{fig:multistep}.
\begin{theorem}[Constructability]\label{thrm:constructability} ~
  \begin{enumerate}[itemsep=0px,partopsep=0px,topsep=0px]
  \item For every $\htau$ there exists $\bar\alpha$ such that
    $\performTypI{\zwsel{\tehole}}{\bar\alpha}{\zwsel{\htau}}$.
